% an ACLU ad recreated in XeLaTeX

\documentclass{article}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{enumitem} % enumerate without space between items
\usepackage{dashbox}


\geometry{
	top=8pt,
	right=8pt,
	left=8pt,
	bottom=8pt,
}

\geometry{
	paperwidth=750pt,
	paperheight=850pt,
}

\renewcommand{\baselinestretch}{1} % line spacing


\begin{document}

\newcommand{\pt}{\hskip 1pt}
\newcommand{\lb}{\linebreak}


\begin{center}
\colorbox{black}{

% actually Neue Haas Unica Bold ?
\setmainfont{Arial Black}
\renewcommand{\baselinestretch}{.8} % line spacing

\begin{minipage}{.98\textwidth}
\color{white}
\fontsize{50}{60}\selectfont
\vspace{50pt}
\begin{center}
There is only\\
one thing that can stop\\
impeachment now.\\
\vspace{10pt}
Your silence.
\vspace{50pt}
\end{center}
\end{minipage}
}
\end{center}

\renewcommand{\baselinestretch}{1}

\color{black}

\setmainfont{Arial}

\parskip 0pt % remove vertical space between paragraphs

\begin{multicols}{3}


Richard Nixon has made one thing perfectly clear.

He will function above the law whenever he can get\linebreak
away with it.

He used illegal wiretaps to spy on newspaper\linebreak
reporters and political opponents until the United\linebreak
States Supreme Court made him stop. He secretly\linebreak
bombed Cambodia until Congress found out and\linebreak
made him stop. He authorized the "plumbers" to \linebreak
burglarize and spy upon his political opponents\linebreak
 until Watergate made him stop. He withheld evi-\linebreak
 dence of criminial activity until a federal court ordered\linebreak
 him to stop. And he defied that court order until\linebreak
 Congress and the people thretened to impeach\linebreak
 him. Then he further obstructed justice by firing\linebreak
 Archibald Cox, the only independent prosecutor\linebreak
 the people had, and turned the Watergate investiga\-tion back to his own Justice Department.

He will continue to violate the Constitution and\linebreak
place himself above the law -- unless we make him\linebreak
stop once and for all.

Impeachment proceedings are already under-\linebreak
way, but many members of the House of Repre-\linebreak
sentatives will find it politically expedient to avoid
action. \textit{Don't let them get away with it.}

It is time to redeem our integrity. It is time to re-\lb
assert our commitment to lawful Constitutional\lb
Government.

Now each of us must choose the kind of country\linebreak
we want. And each member of the House of\linebreak
Representatives must choose between us and\linebreak
Richard Nixon.

If the House of Representatives does not impeach\linebreak
Richard Nixon and thereby bring him to trial before\linebreak
the Senate, it will be because not enough of you\linebreak
have made your voices heard. No vote you have\linebreak
ever cast in any election is more important than the\linebreak
letter you write to your Representative today.

\columnbreak
\begin{center}
\setmainfont{Arial Bold}
Six things you can do now
\end{center}

Here's what you should do before you lay this\lb
newspaper aside:

{\bf 1.} Write your Representative in Congress at:\lb
House of Representatives, Washington, D.C. 20515.\lb
Urge him or her to support impeachment \underline{\textit{now}}. %underline
If\lb
you have already written, write again to say that\lb
recent events have only strengthened your convic-\lb
tion. Representatives pay the most attention to indi-\lb
vidual letters that express your own feelings in your\lb
own words. Other communications are slightly less\lb
effective, but still valuable: telegrams, post cards,\lb
phone calls. Form letters and petitions receive the\lb
least attention. But the important thing is to let them\lb
hear from you, in some form, right now. Let them\lb
know you want them to act, right now.

{\bf 2.} After you write to your own Representative,\lb
write to Peter W. Rodino, Jr., Chairman of the House\lb

\begin{center}
\dashbox{
\begin{minipage}{.85\columnwidth}
\begin{center}
\large
\setmainfont{Arial Black}
American Civil Liberties Union\lb
\setmainfont{Arial}
\small
84 Fifth Avenue, New York, N.Y. 10011

\end{center}

% how can I do that cleanly ?
□\,Enclosed is my contribution of \$\hrulefill \lb
to help the Impeachment Campaign.\\
□\,I want to join ACLU. Credit my contribution\lb
towards membership:\\
□\,\$15 Individual \ □\,\$25 Joint \ □\,More\\
□\,I want to volunteer. Please contact me. \\
Name\hrulefill \\
Address\hrulefill \\
City\hrulefill ~State\hrulefill ~Zip\hrulefill \\
Daytime telephone\hrulefill \\
Evening telephone\hrulefill \lb
\resizebox{\columnwidth}{!}{American Civil Liberties Union: Edward J. Ennis, Chairman; Aryeh Neier, Executive Director}
\end{minipage}
}
\end{center}

\vspace*{\fill}

\columnbreak
\noindent
Judiciary Committee, Washington, D.C. 20515. This\lb
is the committee engaged in the initial impeachment\lb
proceedings. Also write to any members of the\lb
Committee who are from your area. Tell them that\lb
impeachment is your first order of business. Tell\lb
them no other business should come before\lb
impeachment.

The members of the Committee are:
\begin{center}
\resizebox{.9\columnwidth}{!}{
\begin{tabular}{ll}
Peter W. Rodino, Jr. (D-N.J.) & Wayne Owens (D-Utah)\\
Harold D. Donohue (D-Mass.)   & Edward Mezvinsky (D-Iowa)\\
Jack Brooks (D-Tex.)          & Edward Hutchinson (R-Mich.)\\
Robert Kastenmeier (D-Wis.)   & Robert McClory (R-Ill.)\\
Don Edwards (D-Calif.)        & Henry Smith (R-N.Y.)\\
William l.Hungate (D-Mo.)     & Charles Sandman (R-N.J.)\\
John J. Conyers, Jr (D-Mich.) & Tom Railsback (R-Ill.)\\
Joshua Eilberg (D-Pa.)        & Charles Wiggins (R-Calif.)\\
Jerome R. Waldie (D-Calif.)   & David Dennis (R-Ind.)\\
Walters Flowers (D-Ala.)      & Hamilton Fish (R-N.Y.)\\
James Mann (D-S.C.)           & Wiley Mayne (R-Iowa)\\
Paul Sarbanes (D-Md.)         & Lawrence Hogan (R-Md.)\\
John Seiberling (D-Ohio)      & William Keating (R-Ohio)\\
George Danielson (D-Calif.)   & Caldwell Butler (R-Va.)\\
Robert Drinan (D-Mass.)       & William Cohen (R-Maine)\\
Charles Rangel (D-N.Y.)       & Trent Lott (R-Miss.)\\
Barbara Jordan (D-Tex.)       & Harold Froehlich (R-Wis.) \\
Ray Thornton (D-Ark.)         & Carlos Moorhead (R-Calif.)\\
Elizabeth Holtzman (D-N.Y.)   & Joseph J. Maraziti (R-N.J.) \\
\end{tabular}
}
\end{center}

{\bf 3.} Get at least 10 friends to do the same.

{\bf 4.} Fill out the coupon and contribute as gener-\lb
ously as you can. A national campaign for impeach-\lb
ment is extremely costly. It will take pressure from\lb
people in every state to get the House of Represent\lb
atives to act.

{\bf 5.} 
if you can volunteer your time, please let us\lb
know. We can use your help. In New York, call\lb
ACLU at (212) 924-7800, or write 84 Fifth Avenue,\lb
New York, N.Y. 10011. Elsewhere, contact your local\lb
ACLU office.

{\bf 6.} 
If you are not yet a member of ACLU, please\lb
use the coupon to join. We need your support in\lb
this extraordinary campaign for impeachment and\lb
in the day-in day-out defense of the Bill of Rights.\lb
\indent Together, we will win back our country.
\vfill
\end{multicols}
\end{document}
